Motor Vehicle Collisions Reduced Across Toronto During and After the Beginning of the COVID-19 Pandemic

### 2024-01-23 outputs/paper/paper.qmd
Fixed spelling in current paper and fixed README.md formatting

---
title: "Motor Vehicle Collisions Reduced Across Toronto During and After the Beginning of the COVID-19 Pandemic"
author: "Emily Su"
thanks: "Data and code are available at: https://github.com/moonsdust/toronto-collisions"
date: today
date-format: "D MMMM YYYY"
abstract: "As one of the fastest growing cities and densest cities in Canada, road and pedestarian safety are growing concerns in Toronto espically after the COVID-19 Pandemic. This paper looks at trends of collisions from 2017 to 2023 in Toronto neighbourhoods and wards, types of collisions, and the number of pedestrians involved. The results shows that motor vehicle collisions and pedestarian involvement in them have decreased after the pandemic. However, further investigation is needed on the demographics of Toronto areas with high number of motor vehicle collisions."
format:
  pdf:
    toc: true
number-sections: true
bibliography: references.bib
---
```{r}
#| include: false
#| warning: false
#| message: false
#### Preamble ####
# Purpose: To create a graphs of the number of collisions and the types of collisions
# in Toronto in different neighbourhoods from 2017 to 2023.
# Author: Emily Su
# Email: em.su@mail.utoronto.ca
# Date: 23 January 2024
# Prerequisites: All the scripts in the scripts folder have been ran starting from 00-install_packages.R.
```

>>>>

---
title: "Motor Vehicle Collisions Reduced Across Toronto During and After the Beginning of the COVID-19 Pandemic"
author: "Emily Su"
thanks: "Data and code are available at: https://github.com/moonsdust/toronto-collisions"
date: today
date-format: "D MMMM YYYY"
abstract: "As one of the fastest growing cities and densest cities in Canada, road and pedestarian safety are growing concerns in Toronto, especially after the COVID-19 Pandemic. This paper looks at trends of collisions from 2017 to 2023 in Toronto neighbourhoods and wards, types of collisions, and the number of pedestrians involved. The results shows that motor vehicle collisions and pedestrian involvement in them have decreased after the pandemic. However, further investigations is needed on the demographics of Toronto areas with high number of motor vehicle collisions."
format:
  pdf:
    toc: true
number-sections: true
bibliography: references.bib
---
```{r}
#| include: false
#| warning: false
#| message: false
#### Preamble ####
# Purpose: To create a graphs of the number of collisions and the types of collisions
# in Toronto in different neighbourhoods from 2017 to 2023.
# Author: Emily Su
# Email: em.su@mail.utoronto.ca
# Date: 23 January 2024
# Prerequisites: All the scripts in the scripts folder have been ran starting from 00-install_packages.R.
```
